---
title: "p8105_hw1_zj2357"
author: "Zekai Jin"
date: "2022-09-19"
output: github_document
---

First of all, we should include  the libraries we are using and prepare the dataset.
```{r init, message=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
penguins=na.omit(penguins)
```

The penguins dataset consists with `r length(penguins)` columns and `r length(penguins$species)` rows. The heading of the dataset is as follows.
```{r, echo=FALSE}
head(penguins)
```

The columns are _`r colnames(penguins)`_. Among  these columns, the mean flipper length is `r round(mean(penguins$flipper_length_mm),2)`.

We then make a scatter plot between Bill Length and Bill Depth, finding that Bill Height positively correlates with Bill Depth, and the relationship varies between species.
```{r problem_1, warning=FALSE}

penguins_scatter = ggplot(penguins, aes(x=bill_length_mm, y = bill_depth_mm,color=species))+geom_point()+labs(x = "Bill Length(mm)", y = "Bill Depth(mm)")+ggtitle("Scatter plot of Bill Length and Bill Depth")

penguins_scatter

ggsave('plots/penguins_scatter.pdf',plot=penguins_scatter,width=5,height=3)

```


```{r problem_2}


```