---
title: "p8105_hw1_zj2357"
author: "Zekai Jin"
date: "2022-09-19"
output: github_document
---

First of all, we should include  the libraries we are using and prepare the dataset.
```{r init, message=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
penguins = na.omit(penguins)
```

# Problem 1
The penguins dataset consists with `r length(penguins)` columns and `r length(penguins$species)` rows. The heading of the dataset is as follows.
```{r, echo=FALSE}
head(penguins)
```

The columns are _`r colnames(penguins)`_. Among  these columns, the mean flipper length is `r round(mean(penguins$flipper_length_mm),2)`.

We then make a scatter plot between Bill Length and Bill Depth, finding that Bill Height positively correlates with Bill Depth, and the relationship varies between species.
```{r problem_1, warning=FALSE}
penguins_scatter = ggplot(penguins,aes(x = bill_length_mm, y = bill_depth_mm,color = species)) +
  geom_point() + 
  labs(x = "Bill Length(mm)", y = "Bill Depth(mm)") +
  ggtitle("Scatter plot of Bill Length and Bill Depth")

penguins_scatter

ggsave('plots/penguins_scatter.pdf',plot = penguins_scatter,width = 5,height = 3)
```

# Problem 2
Generating required data frame with tibble.
```{r problem_2}
p2_df = tibble(normal = rnorm(10),
             logical = normal > 0,
             character = as.vector(sample(1:10,10),mode = "character"),
             factor = factor(sample(1:3,10,replace = TRUE),levels = c(1,2,3)))

```

Try taking the means of the dataframe. 

```{r problem_2_mean, warning=FALSE}
for (coln in colnames(p2_df)) {
  print(paste("printing column:",coln))
  print(mean(pull(p2_df,var = coln)))
  }
```
Thus, meanapplies to numerical and logical datatypes, but not to character and factor datatypes.
```{r problem_2_convertion, message=FALSE}
for (coln in colnames(p2_df[2:4])) {
  print(as.numeric(pull(p2_df,var = coln)))
  }
```
When converting to numeric data types, logical data is converted to 0/1, characters are converted to numbers or NAs if not possible and factors are converted to their levels. Although it is possible to use `as.numeric` to enable `mean()` function for factor datatype, it is dangerous in most cases.
